---
title: "README"
author: "WWoelmer"
date: "January 31, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

The dataset I will be using in this class is a historical time series dataset of Beaverdam Reservoir a drinking water reservoir in Vinton, VA. Data has been collected by the Carey Lab on a weekly basis in the summer to a monthly basis during winter months from 2013 to present. Variables include nutrient chemistry (nitrogen, phosphorus, and carbon) at the deep hole of the reservoir; water quality variables including conductivity, specific conductivity, dissolved oxygen, pH, chlorophyll, and water temperature from the surface to the bottom of the reservoir; meteorological variables for the region including shortwave radiation, precipitation, windspeeds, and air temperature. 

```{r}


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
